High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 overall.tex
Note about possible new paragraph

On February 2017, PanDA Brokers used almost twice as much total backfill
availability than in any other month (preliminary results for March 2017
displayed in Fig.~\ref{fig:backfill-utilization} confirm this trend). No
relevant code update was made during that period and logs indicated that the
brokers were able to perform faster. This is likely due to hardware upgrades
on the DTNs. The absence of continuous monitoring of those nodes does not
allow to quantify bottlenecks but spot measurements of their load indicate
that a faster CPU and better networking were likely responsible for the
improved performance. Investigations showed an average CPU load of 3.6\% on
the upgraded DTNs, as opposed to the ``high'' utilization reported by OLCF
for the previous DTNs. As such, further hardware upgrades seem unlikely to
improve significantly the performance of PanDA Brokers.

>>>>

On February 2017, PanDA Brokers used almost twice as much total backfill
availability than in any other month (preliminary results for March 2017
displayed in Fig.~\ref{fig:backfill-utilization} confirm this trend). No
relevant code update was made during that period and logs indicated that the
brokers were able to perform faster. This is likely due to hardware upgrades
on the DTNs. The absence of continuous monitoring of those nodes does not
allow to quantify bottlenecks but spot measurements of their load indicate
that a faster CPU and better networking were likely responsible for the
improved performance. Investigations showed an average CPU load of 3.6\% on
the upgraded DTNs, as opposed to the ``high'' utilization reported by OLCF
for the previous DTNs. As such, further hardware upgrades seem unlikely to
improve significantly the performance of PanDA Brokers.\mtnote{Possibly, add
a small paragraph summarizing why at the moment we are consuming up to 30\%
of the available backfill.}
